---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ralget
Ralget creates algebraic graphs in R. 

## Installation
You can install the evelopment version from [GitHub](https://github.com/) with:
``` r
# install.packages("devtools")
devtools::install_github("ianmoran11/ralget")
```
## Example
This is a basic example which shows you how to solve a common problem:
```{r example,echo = FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(tidygraph)
library(ggraph)
library(visNetwork)
library(ralget)
```

# The building blocks of charts 
### Vertices 
Vertices are created with the `v()` function, which takes a name and list of attributes associated with the vertex. 
This creates a ralget/tidygraph object:
```{r echo=TRUE, message=FALSE, warning=FALSE, include = TRUE}
v("x", Latitude=  78.26077, Longitude=  -94.11077)
```

### Combining Vertices 

The `+` operator overlays graphs.

The `*` operator creates a link from each vertex on the right to each vertex on the left. 

```{r echo=FALSE}
p <- v("p"); q <- v("q"); s <- v("s"); r <- v("r"); 
p * q + s
```

```{r echo=FALSE, message=FALSE, warning=FALSE, include = TRUE,fig.height=3, fig.width=3}
(p * q + s) %>% plot()
```


```{r fig.height=5, fig.width=5}
g2 <- q*s+q*r
g1 <- p*q+s
gg <- (g1+g2)
library("patchwork")

 (plot(g1) +  ggtitle('Plot 4') )

  
  plot(g2) + plot(gg)

bind_graphs(
  g1 %>% mutate(graph_name = "g1"),
  g2%>% mutate(graph_name = "g2"),
  gg %>% mutate(graph_name = "g1 + g2")
) %>% 
  plot() + facet_wrap(~graph_name)

```

```{r fig.height=5, fig.width=5}
g3 <- s*r
(g1*g3) %>% plot(loops = T) 
```
