---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ralget
Ralget creates algebraic graphs in R. 

## Installation
You can install the evelopment version from [GitHub](https://github.com/) with:
You can install the evelopment version from [GitHub](https://github.com/) with:
``` r
# install.packages("devtools")
# install.packages("devtools")
devtools::install_github("ianmoran11/ralget")
```
## Example
This is a basic example which shows you how to solve a common problem:
```{r example,echo = FALSE, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(tidygraph)
library(ggraph)
library(patchwork)
devtools::install(); 3
#devtools::install(); 3
library(ralget)
```

# The building blocks of charts 
### Vertices 
Vertices are created with the `v()` function, which takes a name and list of attributes associated with the vertex. 
This creates a ralget/tidygraph object:
```{r echo=TRUE, message=FALSE, warning=FALSE, include = TRUE}
v("x", Latitude=  78.26077, Longitude=  -94.11077)
```

### Combining Vertices 

Take the following vertices:
```{r echo=FALSE}
p <- v("p"); q <- v("q"); s <- v("s"); r <- v("r"); 
```

#### Overlaying graphs ( + )  

The `+` operator overlays graphs.


```{r fig.height=7, fig.width=20}
g2 <- q*s+q*r
g1 <- p*q+s
gg <- (g1+g2)
```
```{r echo=FALSE, message=FALSE, warning=FALSE, include = TRUE, fig.height=7, fig.width=20}
format <- theme(plot.title = element_text(hjust = 0.5)) +  theme(panel.background = element_rect(fill = rgb(.95,.95,.95,1),color = NA)) 
(plot(g1) + ggtitle("g1") + format) +
(plot(g2) + ggtitle("g2") + format) + 
(plot(gg) + ggtitle("g1 + g2") + format) 

```

#### Connecting graphs ( * )  

The `*` operator creates a link from each vertex on the right to each vertex on the left. 
```{r echo=FALSE, message=FALSE, warning=FALSE, include = TRUE, fig.height=7, fig.width=20}
 g3 <- s*r
gg1 <- g1 * g3
(plot(g1) + ggtitle("g1") + format) +
(plot(g3) + ggtitle("g3") + format) + 
(plot(gg1, loops = T) + ggtitle("g1 * g3") + format) 
 ```
